---
title: "DATA_605_Assignment_8_DThonn"
file: DThonn_Assign8_DATA_605
name: Daniel Thonn
output:
  html_document: default
  pdf_document: default
course: DATA 605 CUNY MSDA program
---

** DATA_605_Assignment_8_Thonn - Random Variables  **

http://rpubs.com/danthonn/373453

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``````{r, echo=TRUE}
# install libraries if needed
#install.packages("permutations")
#library(permutations)

#install.packages('gtools')
#library(gtools)

```
Assignment-8:
11 and #14 on page 303 (chapter 7); 1 on page 320-321 (chapter 8)

** Problem-Ch.7 - #11 **

11. A company buys 100 lightbulbs, each of which has an exponential lifetime of 1000 hours. What is the expected time for the first of these bulbs to burn out? (See Exercise 10.)


Answer 7-11:
``````{r, echo=TRUE}
# expected life for first bulbs to burn out

n <- 1000
num_bulbs <- 100
exp_time <- n/num_bulbs
exp_time
# [1] 10


```

** Problem-Ch.7 - #14 **

14. Assume that X1 and X2 are independent random variables, each having an
exponential density with parameter lambda. Show that Z = X1 - X2 has density
fZ(z) = (1/2)  lambda  e ^ (-lambda |z|)

Answer 7-14:

** Note: see example 7.4 in the text (Introduction to Probability (Grinstead,Snell)) **


$$f_Z(z) = (1/2)\lambda e^{-\lambda |z|}$$
# Sum of Two Independent Exponential Random Variables
# See example 7.4 in text page 292. 

$$f_{X}(x) = f_{Y}(x) = \begin{cases} \lambda e^{-\lambda x} & \text{if } x \geq 0 \end{cases}$$


  
# convolution of two exponential densities, page 293 text
$$ fZ (z) =\int_{-\infty}^{\infty} f_{X}(z+y) f_{Y}(y) dy $$



# plug in f(x) and f(y)

$$ fZ (z) =\int_{z}^{0}  \lambda e - \lambda (z+y) \lambda e - \lambda (y) dy $$




# combine and simplify
$$ fZ (z) =\int_{z}^{0}  \lambda 2 e - \lambda |z| dy $$


# integrate 

$$f_Z(z) = \lambda 2 e^{-\lambda |z|}$$

# conclusion  

$$f_{X}(x) = f_{Y}(x) = \begin{cases} (1/2) \lambda e^{-\lambda x} -\lambda |z|  \end{cases}$$



** Problem-Ch.8 - 1 **

1. Let X be a continuous random variable with mean μ = 10 and variance
sigma^2 = 100/3. Using Chebyshev’s Inequality, find an upper bound for the
following probabilities.

(a) P(|X 61 10| >= 2).


``````{r, echo=TRUE}

variance_X <- 100/3
sigma <- sqrt(variance_X)
sigma
# [1] 5.773503

eps <- 2
k <- eps/sigma
k
# [1] 0.3464102

cheby <- pmin(1/k^2, 1)
cheby
## [1] 1

```

(b) P(|X 61 10| >= 5).


``````{r, echo=TRUE}

variance_X <- 100/3
sigma <- sqrt(variance_X)
sigma
# [1] 5.773503

eps <- 5
k <- eps/sigma
k
# [1] 0.8660254

cheby <- pmin(1/k^2, 1)
cheby
# [1] 1

```

(c) P(|X 61 10| >= 9).


``````{r, echo=TRUE}

variance_X <- 100/3
sigma <- sqrt(variance_X)
sigma
# [1] 5.773503

eps <- 9
k <- eps/sigma
k
# [1] 1.558846

cheby <- 1/k^2
cheby
# [1] 0.4115226


```

(d) P(|X 61 10| >= 20).


``````{r, echo=TRUE}

variance_X <- 100/3
sigma <- sqrt(variance_X)
sigma
# [1] 5.773503

eps <- 20
k <- eps/sigma
k
# [1] 3.464102

cheby <- 1/k^2
cheby
# [1] 0.08333333


```




** END **


``````{r, echo=TRUE}

```


